---
output: github_document
---

# detectors

`detectors` is an R data package containing predictions from various GPT detectors. The data is based on the pre-print:

**GPT Detectors Are Biased Against Non-Native English Writers.**
*Weixin Liang*, *Mert Yuksekgonul*, *Yining Mao*, *Eric Wu*, *James Zou.*
arXiv: [2304.02819](https://arxiv.org/abs/2304.02819)

The study authors carried out a series of experiments passing a number of essays to different GPT detection models. Juxtaposing detector predictions for papers written by native and non-native English writers, the authors argue that GPT detectors disproportionately classify real writing from non-native English writers as AI-generated. 

## Installation

You can install the data package with the following code:

```{r load, eval = FALSE}
require(pak)
pak::pak("simonpcouch/detectors")
```

## Example

Taking a look at the data:

```{r print, warning = FALSE, message = FALSE}
library(tidyverse)
library(detectors)

detectors
```

An example plot demonstrates the distributions of predicted probabilities that a text sample was written by AI depending on the GPT detector model and lived experience in writing English of the author:

```{r plot}
detectors %>%
  filter(!is.na(native)) %>%
  ggplot() +
  aes(x = detector, y = .pred_AI, fill = native) +
  geom_violin(bw = .05) +
  labs(
    x = "GPT Detector Tool",
    y = "Predicted Probability That\nSample Was Written by AI",
    fill = "Native\nEnglish\nWriter"
  ) +
  theme_minimal() +
  scale_fill_brewer(type = "qual") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```
