---
output: github_document
---

```{r setup, echo = FALSE} 
should_eval <- "ggplot2" %in% installed.packages()

knitr::opts_chunk$set(eval = should_eval)
```

# detectors

`detectors` is an R data package containing predictions from various GPT detectors. The data is based on the paper:

**GPT Detectors Are Biased Against Non-Native English Writers.**
*Weixin Liang*, *Mert Yuksekgonul*, *Yining Mao*, *Eric Wu*, *James Zou.*
[CellPress Patterns](https://doi.org/10.1016/j.patter.2023.100779).

The study authors carried out a series of experiments passing a number of essays to different GPT detection models. Juxtaposing detector predictions for papers written by native and non-native English writers, the authors argue that GPT detectors disproportionately classify real writing from non-native English writers as AI-generated. 

## Installation

You can install the data package with the following code:

```{r load, eval = FALSE}
require(pak)
pak("simonpcouch/detectors")
```

## Example

Taking a look at the data:

```{r print, eval = FALSE}
library(ggplot2)
library(detectors)

detectors
```

```{r load-pkgs, echo = FALSE, warning = FALSE, message = FALSE, eval = should_eval}
library(ggplot2)
library(detectors)

detectors
```

An example plot demonstrates the distributions of predicted probabilities that a text sample was written by AI depending on the GPT detector model and lived experience in writing English of the author:

```{r plot, fig.alt = "A ggplot side-by-side density plot showing the distributions of predicted probabilities that a text sample was written by AI depending on the GPT detector model and lived experience in writing English of the author. All shown models classify samples written by native English writers well, and do so variably poorly for non-native English writers.", eval = FALSE}
detectors_plot <- 
  detectors[!is.na(detectors$native), ] %>%
  ggplot() +
  aes(x = detector, y = .pred_AI, fill = native) +
  geom_violin(bw = .05) +
  labs(
    x = "GPT Detector Tool",
    y = "Predicted Probability That\nSample Was Written by AI",
    fill = "Native\nEnglish\nWriter"
  ) +
  theme_minimal() +
  scale_fill_brewer(type = "qual") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

detectors_plot
```

```{r, echo = FALSE, eval = FALSE}
ggsave("inst/figures/plot-1.png", detectors_plot)
```

!["A ggplot side-by-side density plot showing the distributions of predicted probabilities that a text sample was written by AI depending on the GPT detector model and lived experience in writing English of the author. All shown models classify samples written by native English writers well, and do so variably poorly for non-native English writers."](inst/figures/plot-1.png)
